Inequalities by ethnicity in the CHD pathway

### 2024-03-06 findings.qmd
Finesse iod and ci chart

@@

@@

>>>>

## Introduction

In the earlier report ..........

## CHD Metrics

jhjkhhjhkj

@@

```{r}
tar_read(ci_iod_chart)
```

@@

## Appendix

### Definitions and data sources of pathway metrics

### Methods explained

#### CHD synthetic prevalence estimates

CHD synthetic prevalence estimates data has been removed from Fingertips by OHID.

OHID have sent the archived data. This is for 7564 practices from 2015, of which 6297 are current practices.

Need to identify practices with missing data and work out how to get a prevalence for them.

Also have file from previous project - checked data is the same but need to check practices included - maybe there are more?

nearest neighbours to impute chd prevalence

#### Census 2021 Ethnicity by LSOA

#### Which date should be used for the gp list size dataset?
